---
title: "Testing Quarto"
title-block-banner: true
author: "Insert Your Name Here"
format: html
editor: source
bibliography: veracruz.bib
---

```{r global_options, include=FALSE, cache=FALSE}
## Set some options for knitr to apply globally
knitr::opts_chunk$set(echo=FALSE,
                      autodep=TRUE,
                      message=FALSE,
                      warning=FALSE,
                      out.width="50%",
                      fig.asp=0.75,
                      fig.align='center')
library(np)
options(np.messages=FALSE)
```

# Introduction

This is my first attempt at using Quarto for reproducible research. For example, see @fig-plot for a bivariate kernel density estimate of a bimodal distribution [@racine_2019].

```{r}
#| label: fig-plot
#| fig-cap: "Plot"
par(cex=0.75)
data(faithful)
fhat <- npudens(~waiting+eruptions,data=faithful)
plot(fhat,xtrim=-0.1,view="fixed",main="")
```

You can do inline math, i.e., $\hat\beta=(X'X)^{-1}X'Y$, or display math, i.e., OLS (@eq-ols) 
 
 $$\hat\beta=(X'X)^{-1}X'Y$$ {#eq-ols} 
 
(display math appears on a separate line from the narrative.)

And you can do inline R computation, e.g., the mean of eruptions is `r pander::pander(mean(faithful$eruptions))` minutes (this valuei was not pre-computed but is extracted from the data used in the above figure as this file is rendered).